% !TEX root = ../../Dissertation.tex

\chapter{List of publications}

\subsection*{Journal Articles Used in This Dissertation}

\begin{enumerate}
    \item \textbf{Pham, L. N.}; Claes, P.; Lievens, P.; Jiang, L.; Wende, T.; Asmis, K. R.; Nguyen, M. T.; Janssens, E. Geometric Structures and Magnetic Interactions in Small Chromium Oxide Clusters. \textit{J. Phys. Chem. C} \textbf{2018}, \textit{122}, 27640 -- 27647.
    \item \textbf{Pham, L. N.}; Nguyen, M. T. Another Look at Photoelectron Spectra of the Anion \ch{Cr2O2-}: Multireference Character and Energetic Degeneracy. \textit{J. Chem. Theory Comput.} \textbf{2018}, \textit{14}, 4833 -- 4843.   
    \item \textbf{Pham, L. N.}; Nguyen, M. T. Insights into Geometric and Electronic Structures of \ch{VGe3$^{-/0}$} Clusters from Anion Photoelectron Spectrum Assignment. \textit{J. Phys. Chem. A} \textbf{2017}, \textit{121}, 6949 -- 6956.
    \item \textbf{Pham, L. N.}; Nguyen, M. T. Titanium Digermanium: Theoretical Assignment of Electronic Transitions Underlying Its Anion Photoelectron Spectrum. \textit{J. Phys. Chem. A} \textbf{2017}, \textit{121}, 1940 -- 1949.
    \item \textbf{Pham, L. N.}; Nguyen, M. T. Electronic Structure of Neutral and Anionic Scandium Disilicon \ch{ScSi2$^{-/0}$} Clusters and the Related Anion Photoelectron Spectrum. \textit{J. Phys. Chem. A} \textbf{2016}, \textit{120}, 9401 -- 9410.
\end{enumerate}

\subsection*{Manuscripts Used in This Dissertation}

\begin{enumerate}
    \item \textbf{Pham, L. N.}; van Dijk, C. N.; Kirilyuk,  A.; Nguyen, M. T.; Janssens, E. et al. Bimetallic Oxide Clusters \ch{Cr_xMn_yO_z+}: Geometric structures, structural evolution, and magnetic properties \textit{Manuscript in preparation}
\end{enumerate}

\subsection*{Others during the PhD Program}


\begin{enumerate}
    \item Jia, M.; van der Tol, J.; Li, Y.; Chernyy, V.; Bakker, J. M.; \textbf{Pham, L. N.}; Nguyen, M. T.; Janssens, E. Structures and Magnetic Properties of Small \ch{Co_n+} and \ch{Co_{n-1}Cr+} ( n = 3 -- 5) Clusters. \textit{J. Phys.: Condens. Matter} \textbf{2018}, \textit{30}, 474002.
    \item Nguyen, T. H. M.; \textbf{Pham, L. N.} et al. An Insight into \ch{C-H...N} Hydrogen Bond and Stability of the Complexes Formed by Trihalomethanes with Ammonia and Its Monohalogenated Derivatives. \textit{Int. J. Quantum Chem.} \textbf{2016}, \textit{117}, e25338.
    \item \textbf{Pham, L. N.}; Hendrickx, M. F. A. Contributions of Nearly Degenerate States to the Photoelectron Spectra of the Vanadium Dicarbide Anion. \textit{J. Phys. Chem. A} \textbf{2016}, \textit{120}, 9465-9475.
\end{enumerate}




\subsection*{Presentations}

\begin{enumerate}
	\item Electronic Transition in Anion Photoelectron Spectra of \ch{VC2-} and \ch{ScSi2-} Clusters, 2nd Annual Meeting and Conference of the European Joint Doctorate in Theoretical Chemistry and Computational Modelling, EJD-TCCM, Leuven Belgium, Poster presentation 2017.
	\item Electronic Structures and Insights into Anion Photoelectron Spectra, WATOC-2017, Munich Germany, Poster presentation 2017.
	%\item Small clusters containing transition metals: Migration from multireference reference methods to DFT approaches, Seminar
\end{enumerate}



