% !TEX root = ../../Dissertation.tex

\chapter*{Preface}                                  \label{ch:preface}

My journey to the end of PhD student life is done after nearly five years of living and studying in Leuven. This is a long run with several different experiences, emotions, memories, and learning. All things harvested during my PhD program were tremendous and super meaningful to me. I would like to express my deep gratitude towards all the individuals making up my PhD journey a success.   


First and foremost, I would like to give special thanks to my supervisor Prof. Minh Tho Nguyen for his excellent support, guidance, patience, and motivation throughout my PhD program in Belgium. Without his invaluable support and efforts, I would not have had the chance to experience scientific life and study at KU Leuven. I will bring every single piece of knowledge learned from my supervisor and his merits of being a professor back to Vietnam and disseminate them to my future students.


I want to show my great thanks to Prof. Ewald Janssens for the fruitful discussions and enthusiastic support over the collaborative projects. I have gained huge experience throughout preparation of manuscripts under his guidance and revisions. These are all highly valuable to me during the PhD program here at KU Leuven.


I am grateful to Prof. Marc Hendrickx for his supervision during my pre-doctoral program. After more than one year of working with him, I have learned many skills and techniques related to computational and quantum chemical research. The skills and knowledge obtained from my pre-doctoral research were helpful for all research projects in my PhD program. 


I truly appreciate Dr. Alex Domingo for his very kind technical support. I have learned from him all basic skills to do computational chemistry, especially how to use the Molcas program. Under Alex's help, I have become more familiar with linux systems, and confident of doing computations and analyzing computational data. I would say that he was a scientific mentor during my first years at KU Leuven.  I also want to thank Tzvetan for his help in dealing with technical problems at the beginning of my pre-doctoral program.


My thanks go to all friends in the Division of Quantum Chemistry and Physical Chemistry who have been creating an amazing atmosphere both on- and off-office: Dragan, Andrea, Carlos, Ana, Tolga, Tuan Anh, Simon, Quan, Xiaoyong, Ewa, Athanasios, Milica, Eliot, Prashant, Jason, May Mee, Hung Hang, Trang, Berna, Cansu, Maike, Zhen, Pierre-Louis, Damiano, Carlo, and some others. I also want to give my sincere thanks to Mrs. Rita Jungbluth and Dr. Hans Vansweevelt for their support and time. 


Thank you Dr. Lars Goerigk for hosting me during the time I was doing my exchange at the University of Melbourne. There I got more opportunities to learn more about computational chemistry, especially double-hybrid density functional theory. At the University of Melbourne I also have more friends such as Nisha and Marcos.

I am indebted to the KU Leuven research Council for a doctoral scholarship within a GOA program on "Quantum Rule on Clusters".

I thank the University of Dalat for making me totally free of any teaching duty, so that I could fully invest my time into doing research at KU Leuven. 

I also want to thank all jury members for their time and energy in evaluation and correction of this thesis. 

\begin{otherlanguage}{vietnamese}
Con xin cảm ơn Ba Má ở nhà rất nhiều vì đã luôn động viên và khuyên bảo con trong suốt quá trình học tập tại Bỉ. Cảm ơn Bố Mẹ đã quan tâm chăm sóc gia đình nhỏ của con trong suốt thời gian con đi học xa nhà. 
\end{otherlanguage}




Last but not least, I have to say that I owe my wife and my daughter the greatest thanks ever for supporting me unconditionally. I have been staying away from my little family for almost 5 years, and my wife has been taking care of our daughter alone for such long time, even though my wife is still doing her PhD research. There are not enough words to show my deep gratitude to her. I love you - my wife - and our family so much. All the time here in Leuven, I just wanted to finish the PhD research as soon as possible and go back to my little family. 





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Keep the following \cleardoublepage at the end of this file, 
% otherwise \includeonly includes empty pages.
\cleardoublepage

% vim: tw=70 nocindent expandtab foldmethod=marker foldmarker={{{}{,}{}}}
